Comparison of Terrain Following and Cut Cell Grids with a Non-Hydrostatic Model

### 2015-02-16 msc-publication.tex
add double height mountain to sample line

\begin{figure}
	\centering
	\includegraphics{../msc-publication-fig-gravityWaves-sampleLine/fig-gravityWaves-sampleLine.pdf}
%
	\caption{Vertical profiles of the Exner function of pressure, \(\Pi\), and potential temperature, \(\theta\), in the gravity waves test.  The computational mode is manifested as a zig-zag in potential temperature on the cut cell grid.  Results on the SLEVE grid (not shown) are qualitatively the same as those on the BTF grid.}
	\label{fig:gw-exner-theta}
\end{figure}

>>>>

\begin{figure}
	\centering
	\includegraphics{../msc-publication-fig-gravityWaves-sampleLine/fig-gravityWaves-sampleLine.pdf}
%
	\caption{Vertical profiles of the Exner function of pressure, \(\Pi\), and potential temperature, \(\theta\), in the gravity waves test.  Exner profile is visually identical on all grids for both mountain heights; for clarity, the Exner profile is only plotted for the BTF grid.  The computational mode is manifested as a zig-zag in potential temperature on the cut cell grid which.  Doubling the mountain height from \SI{250}{\meter} to \SI{500}{\meter} increases the severity of the computational mode but has negligible effect on the BTF grid.  Results on the SLEVE grid (not shown) are qualitatively the same as those on the BTF grid for both mountain heights.}
	\label{fig:gw-exner-theta}
\end{figure}
